Scikit-learn: machine learning without learning the machinery

### 2014-07-01 article.tex
typos

On Fig.\,\ref{fig:random_forest}, we use a popular machine-learning
algorithm, random forests, to predict the wage from the years of
education, or the years of work experience, either as separate features,
or combined. The patchy square appearance of the prediction is due to the
inners of the algorithm, and it illustrates the corresponding
extrapolation mechanism. The predictions fit the data very; maybe too
well, as, on the prediction solely from the years of education (left of
the figure), it is hard to believe in the bump at 5 years. This bump is
probably a classic case of \emph{overfit}: the algorithm is learning its
prediction from noise in the data. As a result, the prediction error on
new data will be significantly different than that measured on the
training data.

@@

Here, we asked the estimator to predict if the reviews were positive for
a batch of two reviews. The first review is predicted has being not
positive, \emph{i.e.} negative, while the second one is positive. We have
anecdotal evidence that the classifier work. To get a measure for the
classifier's accuracy we retrain it in a cross-validation scheme.
This yields the fraction of correct answers on three different folds:
\begin{lstlisting}
>>> from sklearn import cross_validation
>>> cross_validation.cross_val_score(clf, data.data, data.target)
array([0.9026946, 0.8723724, 0.8633634])
\end{lstlisting}

>>>>

On Fig.\,\ref{fig:random_forest}, we use a popular machine-learning
algorithm, random forests, to predict the wage from the years of
education, or the years of work experience, either as separate features,
or combined. The patchy square appearance of the prediction is due to the
inners of the algorithm, and it illustrates the corresponding
extrapolation mechanism. The predictions fit the data well; maybe too
well, as, on the prediction solely from the years of education (left of
the figure), it is hard to believe in the bump at 5 years. This bump is
probably a classic case of \emph{overfit}: the algorithm is learning its
prediction from noise in the data. As a result, the prediction error on
new data will be significantly different than that measured on the
training data.

@@

Here, we asked the estimator to predict if the reviews were positive for
a batch of two reviews. The first review is predicted has being not
positive, \emph{i.e.} negative, while the second one is positive. We have
anecdotal evidence that the classifier works. To get a measure for the
classifier's accuracy we retrain it in a cross-validation scheme.
This yields the fraction of correct answers on three different folds:
\begin{lstlisting}
>>> from sklearn import cross_validation
>>> cross_validation.cross_val_score(clf, data.data, data.target)
array([0.9026946, 0.8723724, 0.8633634])
\end{lstlisting}
